Response to the defense feedback

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

Recent work has made good progress in detecting side-channel leakages automatically. Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites in software products automatically. However, those tools have limitations.

@@

Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores.
The main memory is at the bottom of the memory hierarchy.
\begin{figure}[ht]
  \centering
  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}

@@

\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
Symbolic execution is notorious for its expensive performance cost.
Previous trace-oriented symbolic execution
work~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} has serious
performance bottlenecks. As a result, these approaches either apply only to
small programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or require
domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis.
These tools interpret each
instruction and update memory cells and registers with formulas that
captured the semantics of the execution and search different input values that
can lead to different execution behaviors using a constraint solver.
We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas. While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
We observe that finding side-channels using symbolic execution differs from
traditional symbolic execution, and it can be optimized to be as efficient
as other methods.

>>>>

Recent work has made good progress in detecting side-channel leakages automatically. Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites in software products automatically. However, these tools have limitations.

@@

Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance. Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores.
The main memory is at the bottom of the memory hierarchy.
\begin{figure}[ht]
  \centering
  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with the relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
\end{figure}

@@

\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
Symbolic execution is notorious for its expensive performance cost.
Previous trace-oriented symbolic execution
work~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} has serious
performance bottlenecks. As a result, these approaches either apply only to
small programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or require
domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis.
These tools interpret each
instruction and update memory cells and registers with formulas that
captured the semantics of the execution and search different input values that
can lead to different execution behaviors using a constraint solver.
We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas. While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
We observe that finding side-channels using symbolic execution differs from
traditional symbolic execution, and the symbolic analysis approach can be optimized to be as efficient
as other methods.
